### 2019-04-13 Sections/authors.tex
QI domain update
minor
Editing NL QML
++
Push following CUP proposal resubmission
affils

\boldauthor{Peter P. Rohde {\normalfont(ed.)}}
\email[To whom correspondence should be addressed: ]{dr.rohde@gmail.com}
\homepage{http://www.peterrohde.org}
\smallaffiliation{Centre for Quantum Software \& Information (QSI), Faculty of Engineering \& Information Technology, University of Technology Sydney, NSW 2007, Australia}
\smallaffiliation{Hearne Institute for Theoretical Physics, Louisiana State University, Baton Rouge, LA 70803, United States}

@@

\boldauthor{Zixin Huang}
%\email{zixin.huang@sheffield.ac.uk}
\smallaffiliation{Department of Physics \& Astronomy, University of Sheffield, United Kingdom}

@@

\boldauthor{He-Liang Huang}
%\email{quanhhl@mail.ustc.edu.cn}
\smallaffiliation{Hefei National Laboratory for Physical Sciences at Microscale and Department of Modern Physics, University of Science and Technology of China, Hefei, Anhui 230026, China}
\smallaffiliation{CAS Centre for Excellence and Synergetic Innovation Centre in Quantum Information and Quantum Physics, University of Science and Technology of China, Hefei, Anhui 230026, China}
\smallaffiliation{CAS-Alibaba Quantum Computing Laboratory, Shanghai 201315, China}
\smallaffiliation{Henan Key Laboratory of Quantum Information \& Cryptography, Zhengzhou Information Science and Technology Institute, Zhengzhou, Henan 450000, China}

@@

\boldauthor{Zu-En Su}
%\email{zuensu@gmail.com}
\smallaffiliation{Hefei National Laboratory for Physical Sciences at Microscale and Department of Modern Physics, University of Science and Technology of China, Hefei, Anhui 230026, China}
\smallaffiliation{CAS Centre for Excellence and Synergetic Innovation Centre in Quantum Information and Quantum Physics, University of Science and Technology of China, Hefei, Anhui 230026, China}
\smallaffiliation{CAS-Alibaba Quantum Computing Laboratory, Shanghai 201315, China}

@@

\boldauthor{Simon Devitt}
%\email{simon.devitt@uts.edu.au}
\smallaffiliation{Centre for Quantum Software \& Information (QSI), Faculty of Engineering \& Information Technology, University of Technology Sydney, NSW 2007, Australia}

@@

\boldauthor{Atul Mantri}
%\email{atul\_mantri@mymail.sutd.edu.sg}
\smallaffiliation{Singapore University of Technology \& Design, 20 Dover Dr, Singapore 138682}
\smallaffiliation{Centre for Quantum Technologies, National University of Singapore, Block S15, 3 Science Drive 2, Singapore 117543}

@@

\boldauthor{Si-Hui Tan}
%\email{sihui.tan@gmail.com}
\smallaffiliation{Singapore University of Technology \& Design, 20 Dover Dr, Singapore 138682}

@@

\boldauthor{Nana Liu}
%\email{coronocephalus@gmail.com}
\smallaffiliation{Singapore University of Technology \& Design, 20 Dover Dr, Singapore 138682}

@@

\boldauthor{Scott Harrison}
%\email{harrison@dipf.de}
\smallaffiliation{Leibniz Institute for Research \& Information in Education, Rostocker Stra{\ss}e 6, 60323 Frankfurt am Main, Germany}

@@

\boldauthor{Darryl Vietch}
%\email{darryl.veitch@uts.edu.au}
\smallaffiliation{University of Technology Sydney, NSW 2007, Australia}

@@

\boldauthor{Chandrashekar Radhakrishnan}
%\email{chandrashekar10@gmail.com}
\smallaffiliation{New York University Shanghai, 1555 Century Ave, Pudong, Shanghai 200122, China}

@@

\boldauthor{Jonathan P. Dowling}
%\email{jdowling@lsu.edu}
\smallaffiliation{Hearne Institute for Theoretical Physics and Department of Physics \& Astronomy, Louisiana State University, Baton Rouge, LA 70803, United States}

@@

\boldauthor{Tim Byrnes}
%\email{tim.byrnes@nyu.edu}
\smallaffiliation{State Key Laboratory of Precision Spectroscopy, School of Physical \& Material Sciences, East China Normal University, Shanghai 200062, China}
\smallaffiliation{NYU-ECNU Institute of Physics at NYU Shanghai, 3663 Zhongshan Road North, Shanghai 200062, China}
\smallaffiliation{National Institute of Informatics, 2-1-2 Hitotsubashi, Chiyoda-ku, Tokyo 101-8430, Japan}
\smallaffiliation{New York University Shanghai, 1555 Century Ave, Pudong, Shanghai 200122, China} 
\smallaffiliation{Department of Physics, New York University, New York, NY 10003, United States}

@@

\boldauthor{William J. Munro}
%\email{bill.munro@me.com}
\smallaffiliation{NTT Basic Research Laboratories, 3-1 Morinosato-Wakamiya, Atsugi, Kanagawa 243-0198, Japan}
\smallaffiliation{National Institute of Informatics, 2-1-2 Hitotsubashi, Chiyoda-ku, Tokyo 101-8430, Japan}

>>>>

\if 1\maincontribstyle
\boldauthor{\newline\newline {\footnotesize Main author:}\newline Peter P. Rohde}
\else
\boldauthor{Peter P. Rohde}
\fi
\email[To whom correspondence should be addressed: ]{dr.rohde@gmail.com}
\homepage{http://www.peterrohde.org}
\smallaffiliation{Centre for Quantum Software \& Information (QSI), Faculty of Engineering \& Information Technology, University of Technology Sydney, Australia}
\smallaffiliation{Hearne Institute for Theoretical Physics, Louisiana State University, Baton Rouge, United States}

@@

\if 1\maincontribstyle
\boldauthor{\newline\newline {\footnotesize Contributing authors:}\newline Zixin Huang}
\else
\boldauthor{Zixin Huang}
\fi
%\email{zixin.huang@sheffield.ac.uk}
\smallaffiliation{Department of Physics \& Astronomy, University of Sheffield, United Kingdom}

@@

\boldauthor{He-Liang Huang}
%\email{quanhhl@mail.ustc.edu.cn}
\smallaffiliation{Hefei National Laboratory for Physical Sciences at Microscale and Department of Modern Physics, University of Science \& Technology of China, Hefei, China}
\smallaffiliation{CAS Centre for Excellence and Synergetic Innovation Centre in Quantum Information and Quantum Physics, University of Science \& Technology of China, Hefei, China}
\smallaffiliation{CAS-Alibaba Quantum Computing Laboratory, Shanghai, China}
\smallaffiliation{Henan Key Laboratory of Quantum Information \& Cryptography, Zhengzhou Information Science \& Technology Institute, Zhengzhou, China}

@@

\boldauthor{Zu-En Su}
%\email{zuensu@gmail.com}
\smallaffiliation{Hefei National Laboratory for Physical Sciences at Microscale and Department of Modern Physics, University of Science \& Technology of China, Hefei, China}
\smallaffiliation{CAS Centre for Excellence and Synergetic Innovation Centre in Quantum Information \& Quantum Physics, University of Science \& Technology of China, Hefei, China}
\smallaffiliation{CAS-Alibaba Quantum Computing Laboratory, Shanghai, China}

@@

\boldauthor{Simon Devitt}
%\email{simon.devitt@uts.edu.au}
\smallaffiliation{Centre for Quantum Software \& Information (QSI), Faculty of Engineering \& Information Technology, University of Technology Sydney, Australia}

@@

\boldauthor{Atul Mantri}
%\email{atul\_mantri@mymail.sutd.edu.sg}
\smallaffiliation{Singapore University of Technology \& Design, Singapore}
\smallaffiliation{Centre for Quantum Technologies, National University of Singapore, Singapore}

@@

\boldauthor{Si-Hui Tan}
%\email{sihui.tan@gmail.com}
\smallaffiliation{Singapore University of Technology \& Design, Singapore}

@@

\boldauthor{Nana Liu}
%\email{coronocephalus@gmail.com}
\smallaffiliation{John Hopcroft Center for Computer Science, Shanghai Jiao Tong University, Shanghai, China}

@@

\boldauthor{Scott Harrison}
%\email{harrison@dipf.de}
\smallaffiliation{Leibniz Institute for Research \& Information in Education, Frankfurt am Main, Germany}

@@

\boldauthor{Darryl Vietch}
%\email{darryl.veitch@uts.edu.au}
\smallaffiliation{Faculty of Engineering \& Information Technology, University of Technology Sydney, Australia}

@@

\boldauthor{Chandrashekar Radhakrishnan}
%\email{chandrashekar10@gmail.com}
\smallaffiliation{New York University Shanghai, China}

@@

\boldauthor{Jonathan P. Dowling}
%\email{jdowling@lsu.edu}
\smallaffiliation{Hearne Institute for Theoretical Physics and Department of Physics \& Astronomy, Louisiana State University, Baton Rouge, United States}

@@

\boldauthor{Tim Byrnes}
%\email{tim.byrnes@nyu.edu}
\smallaffiliation{State Key Laboratory of Precision Spectroscopy, School of Physical \& Material Sciences, East China Normal University, Shanghai, China}
\smallaffiliation{NYU-ECNU Institute of Physics at NYU Shanghai, China}
\smallaffiliation{National Institute of Informatics, Tokyo, Japan}
\smallaffiliation{New York University Shanghai, China} 
\smallaffiliation{Department of Physics, New York University, New York, United States}

@@

\boldauthor{William J. Munro}
%\email{bill.munro@me.com}
\smallaffiliation{NTT Basic Research Laboratories, Atsugi, Japan}
\smallaffiliation{National Institute of Informatics, Tokyo, Japan}
